Lattice Boltzmann simulations of magnetically responsive\\ ellipsoidal particle stabilized emulsions

### 2025-03-21 chapters/paper3.tex
Changes 1. Addressed some image sizes and phrasing consistency
Draft 1 complete
Changed I to we in results chapters

In past chapters, I identified the microstructure and particle arrangement of bijels stabilized by ellipsoidal particles under magnetic fields and demonstrated
particles morphology specific ordering to the applied magnetic field. I also show that the local ordering of the particles is affected from the application of
the magnetic field. In this chapter, I probe the dynamics of bijels under constant shear to understand how these microstructural and particle monolayer changes
affect the rheology of bijels stabilized by ellipsoidal particles under magnetic fields. First, I define a shear capillary number 
$Ca_s = \frac{\eta_{f} \dot{\gamma} R_s}{\sigma}$ where $\dot{\gamma} = \frac{2u_{LE}}{L_x}$ is the
strain rate and $R_s$ is the size of equivalent spherical particle. \cite{frijters_effects_2012, yang_capillary_2022} In the literature, $Ca_s$ has been between between 0.04 
and 0.16. However, the box size in these simulations were smaller, meaning that these capillary number ranges would exceed the 
maximum mach number the model allows if this same range were used $(Ma \leq 0.03)$. To accommodate this limitation the 
largest capillary number used will be $Ca_s = 10^-4$ which correspond to a maximum of $Ma \approx 0.02$. As all particles used 
have only hard-sphere type interactions, it is expected that the behaviour seen should mimic 2D colloidal glasses 
percolating in 3D space, akin to what Ching and Mohraz saw, with an additional dependence on the direction of shear. 
This would predict the discovery of particle monolayer dependent elasticity and yield stress along with shear thinning 
behavior of the bijels.

@@

I begin this investigation by analyzing the rheological response of bijels stabilized by ellipsoidal particles under constant shear.
Specifically, I investigate the effect that particle order has on the rheological response characterized. I am also interested in
identifying the impact that the application of magnetic fields have on the rheological response of the bijel. 
Bijel templates simulated in Aim 1 with no field and a field strength of $\bar{B} = 1$ stabilized with a prolate and oblate particles with a 
particle volume fraction $\phi_p = 0.15$ were used as the starting point for these simulations. Next, I apply a field strength of
$\bar{B} = 1$ or switch off the applied field to all structures. This results in four processing setups; $\bar{B}:0\rightarrow 0$, $\bar{B}:0\rightarrow 1$,
$\bar{B}:1\rightarrow 0$ and $\bar{B}:1\rightarrow 1$. I then define a shear capillary number,  $Ca_s = \frac{\dot{\gamma} R_{s} \eta_{f}}{\sigma}$ where 
$\dot{\gamma}$ is the applied strain rate, $R_s$ is the equivalent spherical radius of the particles, $R_s = 7.9$, $\eta_f$ is the dynamic viscosity of the 
fluid and $\sigma$ is the surface tension of the interface. I use five shear numbers, $Ca_s = 1\cdot10^{-4}, 5\cdot10^{-5}, 1\cdot10^{-5}, 5\cdot10^{-6}, 1\cdot10^{-6}$.

@@

The ordering of the particles play an important role in determining the rheology of suspensions as ordered particles can slip over one another
before the structure breaks. The adsorption of particles on the interface of a bijel could affect how this slip occurs. Previous work investigating
the rheology of bijels have determined shear thinning behavior characterized with a Herschel-Buckley fit equation. \cite{macmillan_rheological_2019} 
I perform this analysis on the structures I have simulated. First, I plot the shear stress over time.

@@

Figure \ref{fig:stress_time} shows that there is no definitive steady state value of the shear stress obtained in the simulations performed. This is
attributed to the coarsening of the domains and reorientation of particles at the interface. \cite{tavacoli_novel_2011,macmillan_rheological_2019} 
Tavacoli et al. investigated the rheological response of Ethanediol/Nitromethane bijels and identified that upon placement of a needle to calculate the yield
stress of the bijel, the structure of the material was irreversibly altered. \cite{tavacoli_novel_2011} Macmillian et al. identified that repeated 
shearing of a bijel synthesized using direct mixing resulted in degraded mechanical performance. \cite{macmillan_rheological_2019}
To characterize the viscosity, I identify pseudo-steady state regions within each of the shear stress plots and fit the stress identified within this 
pseudo-steady state region to the strain rate. Pseudo-steady state regions are identified by measuring where the rate of change of shear stress is 
smallest for the longest duration. I fit the calculated stress to the applied strain rate using a Herschel-Buckley rheology model defined as
$\sigma_{xz} = \sigma_{y} + K(\dot{\gamma})^{n}$. $\sigma_{xz}$ is the shear stress calculated from the simulation, $\sigma_{y}$ is the yield stress of the bijel, 
$K$ is the flow consistency index and $n$ is the flow index.Where appropriate, I include results corresponding to a shear capillary number of 
$Ca_s = 10^{-6}$ as in many stress responses, $Ca_s = 10^{-6}$ may not always yield usable results.

\begin{figure} 
    \centering 
    \includegraphics[scale=0.4]{../figures/results/paper3/stress_strain-all.png} 
    \caption{Fitting the experimental shear stress to the strain rate using the Herschel Buckley model. I characterize the bijels are 
             shear thinning in all cases. I show that the bijels become less shear thinning as the particle order increases. I also
             demonstrate that the particle ordering affects the yield stress differently for particles stabilized by oblate and 
             prolate particles.} 
    \label{fig:stress_strain} 
\end{figure}

From Figure \ref{fig:stress_strain}, the slopes of the curve indicate a non-linear shear response to the applied strain rate, suggesting that the rheological properties
are non-Newtonian. Bijels stabilized by prolate and oblate particles also have different shear properties. For bijels stabilized by oblate particles, the stress curves
are more spread out suggesting that there is a larger variance in the properties arising from the change in the initial microstructure of the bijel. From the plot
the increase in particle order reduces the yield stress of the bijel. For bijels stabilized by rod like particles, the stress response of each processing 
condition is closer together, indicating a smaller variation in the response to the applied magnetic field compared to oblate particles. The shear response upon application
of the magnetic field also suggest that increased ordering of prolate particles makes the bijel more resistant to shear. I quantify the Herschel-Buckley fit parameters and 
tabulate the results in Table \ref{table:rheology_fit}.

\begin{table}[h!]
    \centering
    \begin{tabular}{||c c c c c||} 
     \hline
     Processing & $\alpha$ & $n$ & $K \frac{\Delta m (\Delta t)^{n-2}}{\Delta x} $ & $\sigma_{y} \frac{\Delta m}{\Delta x (\Delta t)^2}$ \\ [0.5ex] 
     \hline\hline
     $\bar{B}: 0 \rightarrow 0$ & 0.5 & 0.511 & 0.999 & $7.168 \cdot 10^{-5}$ \\ 
     \hline
     $\bar{B}: 0 \rightarrow 1$ & 0.5 & 0.579 & 0.944 & $4.008 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 0$ & 0.5 & 0.642 & 0.888 & $4.945 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 1$ & 0.5 & 0.637 & 0.914 & $1.715 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 0 \rightarrow 0$ & 2 & 0.561 & 0.965 & $4.618 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 0 \rightarrow 1$ & 2 & 0.609 & 0.944 & $4.101 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 0$ & 2 & 0.597 & 0.899 & $5.025 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 1$ & 2 & 0.606 & 0.885 & $6.435 \cdot 10^{-5}$ \\ [1ex] 
     \hline
    \end{tabular}
    \caption{Hershel Buckley fit parameters for different processing conditions applied to bijels stabilized by ellipsoidal particles.}
    \label{table:rheology_fit}
\end{table}

The results in Table \ref{table:rheology_fit} show that bijels remain shear thinning regardless of the processing history and particle morphology.
The particle morphology dependent differences in the shear response characterized in Figure \ref{fig:stress_strain} are quantified in Table \ref{table:rheology_fit}
where the yield stress differences predicted is clear to see. I also show that bijel templates with an applied field of $\bar{B} = 1$ have larger flow indices \
than bijel templates made with no applied field. The same trend exists here where the application of a magnetic field makes the bijel more Newtonian. I also 
characterize that the yield stress of bijels stabilized with oblate particles decrease as the initial order of the particles and the applied field onto the bijel increase. 
The yield stress of bijels stabilized by prolate particles increases as the initial order of the particles and the applied field onto the bijel increase. In previous aims, I 
characterized that application of magnetic fields created orientational ordering of the bijels and that the local ordering of the bijels change. I 
showed that as magnetic fields were applied, oblate particles have lower local ordering on the interface while for prolate particles it increases.
Past investigations have identified that particle monolayers buckle more easily as local particle ordering decreases. \cite{prakash_buckling_2024} 
They identified that local ordering can enhance stress distribution among particles, making locally ordered particle monolayers better at withstanding shear.
I visualize the ordering of the particles at the interface to the z direction for both particle morphologies at $Ca_s = 10^{-6}$ for the 
case $\bar{B}: 1 \rightarrow 0$.

@@

In Figure \ref{fig:particle_viz_tz}, the particles are initially ordered to the direction of the applied magnetic field. Upon application of shear and removal
of the magnetic field, I see that the particles begin reorienting away from the z direction. I also observe that the reorientation of particles uncovers the interface.
The reorientation observed is particle morphology specific with prolate particles seeing more reorientation away from the applied shear direction than oblate particles.
Looking at the images, I see that prolate particles rotate away from the direction of the magnetic field and applied shear towards the direction of the shear gradient,
while oblate particles reorient towards minimizing area to the applied shear direction. While these snapshots show the initial and final orientations of the particles at the
interface, the time evolution of the particle monolayer changes to identify its role in the rheological properties characterized.

@@

Particles at the interface of bijels stabilized with ellipsoidal particles reorient at the interface to minimize interfacial and
steric energies. \cite{gunther_timescales_2014} The particles stabilizing bijels in confined systems under shear have been shown to
orient to the direction of shear and ejected from the interface at sufficiently long times or shear.\cite{bonaccorso_shear_2020} 
I probe these aspects of the particle monolayer in this section. I plot the orientation of the particle to each cartesian axis 
to identify if I characterize shear induced ordering.

\begin{figure} 
    \centering 
    \includegraphics[scale=0.3]{../figures/results/paper3/angle_to_cartesian-SS.png} 
    \caption{Comparisons of the initial and final particle orientations of the particles to each cartesian direction under
             four processing histories for bijels stabilized with oblate and prolate ellipsoids at multiple shear rates. I show
             shear dependent ordering of the particle monolayer if the initial particle monolayer begins with particle order.} 
    \label{fig:particle_orientation_cartesian_shear} 
\end{figure}

From Figure \ref{fig:particle_orientation_cartesian_shear} I see that with bijel templates simulated under $\bar{B} = 0$, the
particles adopt a random orientation. Upon application of shear, I see that there is little directional ordering to the 
shear direction in the simulation time observed. Upon application of the magnetic field in the $\bar{B}:0 \rightarrow 1$ case, 
the particles order to the direction of the magnetic field. Here we see that the prolate particles order more readily to the applied
field than the oblate particles, seen as a larger clustering of particles at the $\theta_z = 0$ corner of the triangle. In the 
$\bar{B}:1 \rightarrow 0$ case particle morphology dependent partial relaxation of the particles away from the magnetic field direction 
is observed. Directionality of the particles to the field is still observed, suggesting that the ordering of the particles is not
immediately removed once the field is switched off. In the processing history of $\bar{B}:1 \rightarrow 1$, particles are locked
into ordering to the magnetic field direction. However we also see that some particles are reoriented away from the field direction
due to the applied shear. Prolate particles have a smaller distribution of particle orientations than oblate particles, suggesting that
the initial orientation and ordering of particles to the shear applied underpin the response observed. As the particles are adsorbed on the 
interface, the orientation of the particles are influenced by a balance between magnetic forces from the field and capillary forces 
from the interface. We can qualitatively calculate the time evolution of the capillary interactions using the interfacial angle.

\begin{figure} 
    \centering 
    \includegraphics[scale=0.3]{../figures/results/paper3/psi-time_compare.png} 
    \caption{Comparisons of the interfacial angle of bijels stabilized by ellipsoidal particles as a function of 
             the applied shear rate at four different processing histories. I show that upon application of shear
             particles tilt out of the interface reduces the interfacial area stabilized. $\bar{B}: 0 \to 1$ shows 
             large variations in the interface angle.} 
    \label{fig:interface_angle_shear} 
\end{figure}

From Figure \ref{fig:interface_angle_shear}, I demonstrate that there is a slow increase in the interface angle over time for all cases
except for $\bar{B}: 0 \to 1$. For the $\bar{B}: 0 \to 1$ case, this has been shown in Chapter \ref{chapter:aim2} to be due to particle
reorientation to the applied magnetic field. For all other cases, we see an average increase in $\langle \psi \rangle$ over time, showing
that the particles under shear reorient out of the interface. Particles reorienting out of the interface can be due to shear induced interfacial 
stress, modifying the curvature of the interface and thus the lowest energy particle orientation to the interface or shear induced increases in
interparticle forces, causing the particle to tilt out of the interface to minimize interparticle forces. The latter 
mechanism can be characterized through measurements of the number of particles on the interface as increases in interparticle forces result in ejection of
particles from the interface.

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.3]{../figures/results/paper3/n_int-time_compare.png} 
    \caption{Comparisons of the proportion of particles on the interface of bijels ($n_{int}$) stabilized by ellipsoidal particles as a function of 
             the applied shear rate at four different processing histories. I show that upon application of shear, many cases have a 
             reduction in the number of particles on the interface while in others it stays the same. For cases where $n_{int}$ reduces, I can 
             attribute the domain size coarsening to this effect.} 
    \label{fig:particles_interface_prop_shear} 
\end{figure}

From the results in Figure \ref{fig:particles_interface_prop_shear}, the impact of the initial microstructure on the number of particles on the interface
differs for bijels stabilized by oblate and prolate ellipsoids. I split this analysis on processing history. While keeping the applied magnetic field
the same, little differences in the behavior of $n_{int}$ is observed, with small changes also being characterized for $\langle \psi \rangle$. 
Looking at the case of $\bar{B}:0 \rightarrow 0$, there is little change in the number of particles at the interface upon application of shear. This implies that the 
particles remain strongly adsorbed on the
interface. The $\langle \psi \rangle$ results also show this as this parameter increases slowly. This suggests that the particles remain firmly adsorbed
on the interface. Looking to the $\bar{B}:0 \rightarrow 1$ case, the number of particles at the interface drops while $\langle \psi \rangle$ increases. This
trend affects both particles which suggests that shear can pull particles out of the interface due to the decreased
interfacial adsorption energy the particle experiences when rotating out of the interface to orient to the applied field. The $\bar{B}:1 \rightarrow 1$ and 
$\bar{B}:1 \rightarrow 0$ have strong dependences on particle morphology. While an increase in $\langle \psi \rangle$ can be seen in both processing histories 
for both particle morphologies, a decrease in $n_{int}$ can be seen for prolate particles with processing history $\bar{B}:1 \rightarrow 0$ and for 
oblate particles with processing history $\bar{B}:1 \rightarrow 1$. We visualize $\langle \psi \rangle$ at the initial and final timestep for bijels stabilized with
oblate and prolate particles with processing $\bar{B}:1 \rightarrow 0$.

@@

Figure \ref{fig:particle_viz_psi} shows that the increase in $\langle \psi \rangle$ seen in Figure \ref{fig:interface_angle_shear} occurs due to different
reasons for both particle morphologies. For oblate particles, this is caused by particles orienting such that their symmetry axis is parallel to the interface
while prolate particles experienced interparticle forces induced by the applied shear, resulting in particles being ejected from the interface when the magnetic 
field is switched off. When keeping the magnetic field on, the oblate particles are forced to stay in sub-optimal particle orientations to the interface, resuling
in ejection of particles from the interface. The presence of the magnetic field reduces shear induced interparticle interactions owing to the ordering of
particles to the applied field, resulting in the mostly unchanged $n_{int}$ values. A increase in $\langle \psi \rangle$ and decrease in $n_{int}$ indicates domain
can indicate coarsening of the fluid domains as the interfacial area is reduced. In the next section, I investigate the the role of the interface properties and the 
impact of particle ejection and tilting of particles out of the interface on the microstructure of bijels.

@@

Bonaccorso et al. identified that the spherical particle stabilizers in their bijel simulations oriented to the direction of shear before being
ejected from the interface. \cite{bonaccorso_shear_2020} This then led to the domains of the bijel to coalesce and eventually destruction of the
bicontinuous microstructure. \cite{bonaccorso_shear_2020} In our bijels, we characterize particle morphology and initial microstructure specific 
properties of the particle monolayer upon application of shear. 
In this section, I probe the effect of applied shear to the microstructure of magnetically
responsive bijels stabilized by ellipsoidal particles. To investigate the effect of the particle angle and the interfacial coverage of the bijel on the
microstructural evolution of the interface, I plot the area averaged gaussian curvature over time. This parameter will allow insight into the evolution 
of the interface, namely the presence of domain coarsening, coalscence or break-off events.

\begin{figure} 
    \centering 
    \includegraphics[scale=0.3]{../figures/results/paper3/gaussian-time_compare.png} 
    \caption{Plots of the time evolution of the area averaged Gaussian curvature $\langle K \Sigma^{-2} \rangle$ for four 
             processing histories applied to bijels stabilized with oblate and prolate ellipsoids. I demonstrate that the 
             magnitude of the gaussian curvature reduces for all systems except for $\bar{B}: 0 \to 1$.} 
    \label{fig:gaussian_curvature_time_shear} 
\end{figure}

>>>>

In past chapters, we identified the microstructure and particle arrangement of bijels stabilized by ellipsoidal particles under magnetic fields and demonstrated
particles morphology specific ordering to the applied magnetic field. We also show that the local ordering of the particles is affected from the application of
the magnetic field. In this chapter, We probe the dynamics of bijels under constant shear to understand how these microstructural and particle monolayer changes
affect the rheology of bijels stabilized by ellipsoidal particles under magnetic fields. First, we define a shear capillary number, $Ca_s$
which in the literature lies 0.04 and 0.16. \cite{frijters_effects_2012, yang_capillary_2022}
However, these capillary number ranges would exceed the 
maximum mach number the model allows if this same range were used $(Ma \leq 0.03)$. To accommodate this limitation the 
largest capillary number used will be $Ca_s = 10^-4$ which correspond to a maximum of $Ma \approx 0.02$. As all particles used 
have only hard-sphere type interactions, it is expected that the behaviour seen should mimic 2D colloidal glasses 
percolating in 3D space, akin to what Ching and Mohraz saw, with an additional dependence on the direction of shear. 
This would predict the discovery of particle monolayer dependent elasticity and yield stress along with shear thinning 
behavior of the bijels.

@@

We begin this investigation by analyzing the rheological response of bijels stabilized by ellipsoidal particles under constant shear.
Specifically, we investigate the effect that particle order has on the rheological response characterized. We are also interested in
identifying the impact that the application of magnetic fields have on the rheological response of the bijel. 
Bijel templates simulated in Aim 1 with no field and a field strength of $\bar{B} = 1$ stabilized with a prolate and oblate particles with a 
particle volume fraction $\phi_p = 0.15$ were used as the starting point for these simulations. Next, we apply a field strength of
$\bar{B} = 1$ or switch off the applied field to all structures. This results in four processing setups; $\bar{B}:0\rightarrow 0$, $\bar{B}:0\rightarrow 1$,
$\bar{B}:1\rightarrow 0$ and $\bar{B}:1\rightarrow 1$. We then define a shear capillary number,  $Ca_s = \frac{\dot{\gamma} R_{s} \eta_{f}}{\sigma}$ where 
$\dot{\gamma}$ is the applied strain rate, $R_s$ is the equivalent spherical radius of the particles, $R_s = 7.9$, $\eta_f$ is the dynamic viscosity of the 
fluid and $\sigma$ is the surface tension of the interface. We use five shear capillary numbers, 
$Ca_s = 1\cdot10^{-4}, 5\cdot10^{-5}, 1\cdot10^{-5}, 5\cdot10^{-6}, 1\cdot10^{-6}$.

@@

The ordering of the particles play an important role in determining the rheology of suspensions as ordered particles can slip over one another
before the structure breaks. The adsorption of particles on the interface of a bijel could affect how this slip occurs. Previous work investigating
the rheology of bijels have determined shear thinning behavior characterized with a Herschel-Buckley fit equation. \cite{macmillan_rheological_2019} 
After applying shear on the bijel templates, we characterize and plot the time evolution of the the shear stress in Figure \ref{fig:stress_time}.

@@

Figure \ref{fig:stress_time} shows that there is no definitive steady state value of the shear stress obtained in the simulations performed. This is
attributed to the coarsening of the domains and reorientation of particles at the interface. \cite{tavacoli_novel_2011,macmillan_rheological_2019} 
Tavacoli et al. investigated the rheological response of Ethanediol/Nitromethane bijels and identified that upon placement of a needle to calculate the yield
stress of the bijel, the structure of the material was irreversibly altered. \cite{tavacoli_novel_2011} Macmillian et al. identified that repeated 
shearing of a bijel synthesized using direct mixing resulted in degraded mechanical performance. \cite{macmillan_rheological_2019}
To characterize the fit, we identify pseudo-steady state regions within each of the shear stress plots and fit the stress identified within this 
pseudo-steady state region to the strain rate. Pseudo-steady state regions are identified by measuring where the rate of change of shear stress is 
smallest for the longest duration. We fit the calculated stress to the applied strain rate using a Herschel-Buckley rheology model defined as
$\sigma_{xz} = \sigma_{y} + K(\dot{\gamma})^{n}$. $\sigma_{xz}$ is the shear stress calculated from the simulation, $\sigma_{y}$ is the yield stress of the bijel, 
$K$ is the flow consistency index and $n$ is the flow index. Where appropriate, we include results corresponding to a shear capillary number of 
$Ca_s = 10^{-6}$ as in many stress responses, $Ca_s = 10^{-6}$ may not always yield usable results.

\begin{figure} 
    \centering 
    \includegraphics[scale=0.4]{../figures/results/paper3/stress_strain-all.png} 
    \caption{Fitting the experimental shear stress to the strain rate using the Herschel Buckley model. We characterize the bijels are 
             shear thinning in all cases and that the bijels become less shear thinning as the particle order increases. We also
             demonstrate that the particle ordering affects the yield stress differently for particles stabilized by oblate and 
             prolate particles.} 
    \label{fig:stress_strain} 
\end{figure}

From Figure \ref{fig:stress_strain}, the slopes of the curve indicate a non-linear shear response to the applied strain rate, suggesting that the rheological properties
are non-Newtonian. Bijels stabilized by prolate and oblate particles also have different shear properties. For bijels stabilized by oblate particles, the stress curves
are more spread out suggesting that there is a larger variance in the properties arising from the change in the initial microstructure of the bijel. From the plot
the increase in particle order reduces the yield stress of the bijel. For bijels stabilized by rod like particles, the stress response of each processing 
condition is closer together, indicating a smaller variation in the response to the applied magnetic field compared to oblate particles. The shear response upon application
of the magnetic field also suggest that increased ordering of prolate particles makes the bijel more resistant to shear. We quantify the Herschel-Buckley fit parameters and 
tabulate the results in Table \ref{table:rheology_fit}.

\begin{table}[h!]
    \centering
    \renewcommand{\arraystretch}{1.5}  % Increases row height
    \begin{tabular}{||c c c c c||} 
     \hline
     Processing & $\alpha$ & $n$ & $K \frac{\Delta m (\Delta t)^{n-2}}{\Delta x} $ & $\sigma_{y} \frac{\Delta m}{\Delta x (\Delta t)^2}$ \\ [0.5ex] 
     \hline\hline
     $\bar{B}: 0 \rightarrow 0$ & 0.5 & 0.511 & 0.999 & $7.168 \cdot 10^{-5}$ \\ 
     \hline
     $\bar{B}: 0 \rightarrow 1$ & 0.5 & 0.579 & 0.944 & $4.008 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 0$ & 0.5 & 0.642 & 0.888 & $4.945 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 1$ & 0.5 & 0.637 & 0.914 & $1.715 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 0 \rightarrow 0$ & 2 & 0.561 & 0.965 & $4.618 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 0 \rightarrow 1$ & 2 & 0.609 & 0.944 & $4.101 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 0$ & 2 & 0.597 & 0.899 & $5.025 \cdot 10^{-5}$ \\
     \hline
     $\bar{B}: 1 \rightarrow 1$ & 2 & 0.606 & 0.885 & $6.435 \cdot 10^{-5}$ \\ [1ex] 
     \hline
    \end{tabular}
    \caption{Hershel Buckley fit parameters for different processing conditions applied to bijels stabilized by ellipsoidal particles.}
    \label{table:rheology_fit}
\end{table}

The results in Table \ref{table:rheology_fit} show that bijels remain shear thinning regardless of the processing history and particle morphology.
The particle morphology dependent differences in the shear response characterized in Figure \ref{fig:stress_strain} are quantified in Table \ref{table:rheology_fit}
where the yield stress differences predicted is clear to see. The bijel templates with an applied field of $\bar{B} = 1$ have larger flow indices
than bijel templates made with no applied field. The same trend exists here where the application of a magnetic field makes the bijel more Newtonian.
The yield stress of bijels stabilized with oblate particles decrease as the initial order of the particles and the applied field onto the bijel increase. 
The yield stress of bijels stabilized by prolate particles increases as the initial order of the particles and the applied field onto the bijel increase. In previous aims, we 
characterized that application of magnetic fields created orientational ordering of the bijels and that the local ordering of the bijels change. We  
showed that as magnetic fields were applied, oblate particles have lower local ordering on the interface while for prolate particles it increases.
Past investigations have identified that particle monolayers buckle more easily as local particle ordering decreases. \cite{prakash_buckling_2024} 
They identified that local ordering can enhance stress distribution among particles, making locally ordered particle monolayers better at withstanding shear.
We visualize the ordering of the particles at the interface to the z direction for both particle morphologies at $Ca_s = 10^{-6}$ for the 
case $\bar{B}: 1 \rightarrow 0$.

@@

In Figure \ref{fig:particle_viz_tz}, the particles are initially ordered to the direction of the applied magnetic field. Upon application of shear and removal
of the magnetic field, We see that the particles begin reorienting away from the z direction. We also observe that the reorientation of particles uncovers the interface.
The reorientation observed is particle morphology specific with prolate particles seeing more reorientation away from the applied shear direction than oblate particles.
Looking at the images, we see that prolate particles rotate away from the direction of the magnetic field and applied shear towards the direction of the shear gradient,
while oblate particles reorient towards minimizing area to the applied shear direction. While these snapshots show the initial and final orientations of the particles at the
interface, the time evolution of the particle monolayer changes to identify its role in the rheological properties characterized.

@@

Particles at the interface of bijels stabilized with ellipsoidal particles reorient at the interface to minimize interfacial and
steric energies. \cite{gunther_timescales_2014} The particles stabilizing bijels in confined systems under shear have been shown to
orient to the direction of shear and ejected from the interface at sufficiently long times or shear.\cite{bonaccorso_shear_2020} 
We probe these aspects of the particle monolayer in this section. First, we plot the orientation of the particle to each cartesian axis 
to identify if shear induced ordering is present.

\begin{figure} 
    \centering 
    \includegraphics[scale=0.3]{../figures/results/paper3/angle_to_cartesian-SS.png} 
    \caption{Comparisons of the initial and final particle orientations of the particles to each cartesian direction under
             four processing histories for bijels stabilized with oblate and prolate ellipsoids at multiple shear rates. We show
             shear dependent ordering of the particle monolayer if the initial particle monolayer begins with particle order.} 
    \label{fig:particle_orientation_cartesian_shear} 
\end{figure}

From Figure \ref{fig:particle_orientation_cartesian_shear} we see that with bijel templates simulated under $\bar{B} = 0$, the
particles adopt a random orientation. Upon application of shear, we see that there is little directional ordering to the 
shear direction in the simulation time observed. Upon application of the magnetic field in the $\bar{B}:0 \rightarrow 1$ case, 
the particles order to the direction of the magnetic field. Here we see that the prolate particles order more readily to the applied
field than the oblate particles, seen as a larger clustering of particles at the $\theta_z = 0$ corner of the triangle. In the 
$\bar{B}:1 \rightarrow 0$ case particle morphology dependent partial relaxation of the particles away from the magnetic field direction 
is observed. Directionality of the particles to the field is still observed, suggesting that the ordering of the particles is not
immediately removed once the field is switched off. In the processing history of $\bar{B}:1 \rightarrow 1$, particles are locked
into ordering to the magnetic field direction. However we also see that some particles are reoriented away from the field direction
due to the applied shear. Prolate particles have a smaller distribution of particle orientations than oblate particles, suggesting that
the initial orientation and ordering of particles to the shear applied underpin the response observed. As the particles are adsorbed on the 
interface, the orientation of the particles are influenced by a balance between magnetic forces from the field and capillary forces 
from the interface. We can qualitatively calculate the time evolution of the capillary interactions using the interfacial angle.

\begin{figure} 
    \centering 
    \includegraphics[scale=0.3]{../figures/results/paper3/psi-time_compare.png} 
    \caption{Comparisons of the interfacial angle of bijels stabilized by ellipsoidal particles as a function of 
             the applied shear rate at four different processing histories. We show that upon application of shear
             particles tilt out of the interface reduces the interfacial area stabilized. $\bar{B}: 0 \to 1$ shows 
             large variations in the interface angle.} 
    \label{fig:interface_angle_shear} 
\end{figure}

From Figure \ref{fig:interface_angle_shear}, we demonstrate that there is a slow increase in the interface angle over time for all cases
except for $\bar{B}: 0 \to 1$. For the $\bar{B}: 0 \to 1$ case, this has been shown in Chapter \ref{chapter:aim2} to be due to particle
reorientation to the applied magnetic field. For all other cases, we see an average increase in $\langle \psi \rangle$ over time, showing
that the particles under shear reorient out of the interface. Particles reorienting out of the interface can be due to shear induced interfacial 
stress, modifying the curvature of the interface and thus the lowest energy particle orientation to the interface or shear induced increases in
interparticle forces, causing the particle to tilt out of the interface to minimize interparticle forces. The latter 
mechanism can be characterized through measurements of the number of particles on the interface as increases in interparticle forces result in ejection of
particles from the interface.

@@

\begin{figure} 
    \centering 
    \includegraphics[scale=0.3]{../figures/results/paper3/n_int-time_compare.png} 
    \caption{Comparisons of the proportion of particles on the interface of bijels ($n_{int}$) stabilized by ellipsoidal particles as a function of 
             the applied shear rate at four different processing histories. We show that upon application of shear, many cases have a 
             reduction in the number of particles on the interface while in others it stays the same. 
            %  For cases where $n_{int}$ reduces, I can 
            %  attribute the domain size coarsening to this effect.
             } 
    \label{fig:particles_interface_prop_shear} 
\end{figure}

From the results in Figure \ref{fig:particles_interface_prop_shear}, the impact of the initial microstructure on the number of particles on the interface
differs for bijels stabilized by oblate and prolate ellipsoids. We split this analysis on processing history. While keeping the applied magnetic field
the same, little differences in the behavior of $n_{int}$ is observed, with small changes also being characterized for $\langle \psi \rangle$. 
Looking at the case of $\bar{B}:0 \rightarrow 0$, there is little change in the number of particles at the interface upon application of shear. This implies that the 
particles remain strongly adsorbed on the
interface. The $\langle \psi \rangle$ results also show this as this parameter increases slowly. This suggests that the particles remain firmly adsorbed
on the interface. Looking to the $\bar{B}:0 \rightarrow 1$ case, the number of particles at the interface drops while $\langle \psi \rangle$ increases. This
trend affects both particles which suggests that shear can pull particles out of the interface due to the decreased
interfacial adsorption energy the particle experiences when rotating out of the interface to orient to the applied field. The $\bar{B}:1 \rightarrow 1$ and 
$\bar{B}:1 \rightarrow 0$ have strong dependences on particle morphology. While an increase in $\langle \psi \rangle$ can be seen in both processing histories 
for both particle morphologies, a decrease in $n_{int}$ can be seen for prolate particles with processing history $\bar{B}:1 \rightarrow 0$ and for 
oblate particles with processing history $\bar{B}:1 \rightarrow 1$. We visualize $\langle \psi \rangle$ at the initial and final timestep for bijels stabilized with
oblate and prolate particles with processing $\bar{B}:1 \rightarrow 0$.

@@

Figure \ref{fig:particle_viz_psi} shows that the increase in $\langle \psi \rangle$ seen in Figure \ref{fig:interface_angle_shear} occurs due to different
reasons for both particle morphologies. For oblate particles, this is caused by particles orienting such that their symmetry axis is parallel to the interface
while prolate particles experienced interparticle forces induced by the applied shear, resulting in particles being ejected from the interface when the magnetic 
field is switched off. When keeping the magnetic field on, the oblate particles are forced to stay in sub-optimal particle orientations to the interface, resuling
in ejection of particles from the interface. The presence of the magnetic field reduces shear induced interparticle interactions owing to the ordering of
particles to the applied field, resulting in the mostly unchanged $n_{int}$ values. A increase in $\langle \psi \rangle$ and decrease in $n_{int}$ indicates domain
can indicate coarsening of the fluid domains as the interfacial area is reduced. In the next section, we investigate the the role of the interface properties and the 
impact of particle ejection and tilting of particles out of the interface on the microstructure of bijels.

@@

Bonaccorso et al. identified that the spherical particle stabilizers in their bijel simulations oriented to the direction of shear before being
ejected from the interface. \cite{bonaccorso_shear_2020} This then led to the domains of the bijel to coalesce and eventually destruction of the
bicontinuous microstructure. \cite{bonaccorso_shear_2020} In our bijels, we characterize particle morphology and initial microstructure specific 
properties of the particle monolayer upon application of shear. 
In this section, we probe the effect of applied shear to the microstructure of magnetically
responsive bijels stabilized by ellipsoidal particles. To investigate the effect of the particle angle and the interfacial coverage of the bijel on the
microstructural evolution of the interface, we plot the area averaged gaussian curvature over time. This parameter will allow insight into the evolution 
of the interface, namely the presence of domain coarsening, coalscence or break-off events.

\begin{figure} 
    \centering 
    \includegraphics[scale=0.3]{../figures/results/paper3/gaussian-time_compare.png} 
    \caption{Plots of the time evolution of the area averaged Gaussian curvature $\langle K \Sigma^{-2} \rangle$ for four 
             processing histories applied to bijels stabilized with oblate and prolate ellipsoids. We demonstrate that the 
             magnitude of the gaussian curvature reduces for all systems except for $\bar{B}: 0 \to 1$.} 
    \label{fig:gaussian_curvature_time_shear} 
\end{figure}
